\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-02-13 eg6-letters/NIM/EG6_RTPC_NIM.tex
add noise text, change all $He$ to He

The first implementation of a radial TPC with JLab-CLAS spectrometer has been 
performed by the BoNuS experiment \cite{BONUS} in 2005. The success of the 
BoNuS-RTPC in detecting the slow protons motivated the development of this new 
RTPC. For the channels of interest in CLAS-EG6 experiment, the recoiled 
$^{4}He$ nuclei have momentum per charge around 150 MeV/c. The detection of 
these low-energy nuclei was the primary motivation for designing this detector.

\section{CLAS-EG6 RTPC design} \label{sec_design}
The design of CLAS-EG6 RTPC has been chosen according to physics and 
experimental considerations. At 6 GeV incident electron beam energy, the recoil 
$^{4}He$ nuclei, from the coherent DVCS channel, have an average momentum (per 
charge) around 125 MeV/c, while the "standard" CLAS detects charged particles 
with a threshold of 250 MeV/c. On the experimental site, the chosen design has 
to fit within the available space inside a 5 Tesla Solenoid magnet that 
surrounds the target \cite{Hyon-suk}. Figure \ref{fig:RTPC2} shows an 
experimental view of the RTPC before being inserted into the solenoid.

@@

   \item The first gas gap extends from 3 mm to 20 mm radial distances. It is 
      filled with $^{4}He$ gas at 1~atm. During run, this region is swarmed by 
      M\o ller electrons induced by the beam, such that filling this region 
      with a light gas like $^{4}He$ minimizes secondary interactions. This 
      region is surrounded by a 4 $\mu$m thick window made of aluminized Mylar 
      and connected to ground.                                                                
   \item The gap region extends between 20~mm and 30~mm and is filled with a 
      gas mixture of 80$\%$ Neon and 20$\%$ Dimethyl Ether (DME). This region 
      is surrounded by a 4~$\mu$m thick window made of aluminized Mylar, which 
      serves as the cathode.

@@

We can measure the drift speed using the tracks detected in the RTPC, in figure 
\ref{fig:RTPC_signals} we represent a typical $^{4}He$ track (in green). After 
it causes ionization in the drift region, the released electrons (in black) 
drift to the detection plane under the effect of the electric field. The 
electrons released close to the cathode take the most time to reach the readout 
pads while the geometrical symmetry insure they always travel the same 
distance. So by identifying the maximum TDC measured, we can infer the drift 
speed of the electrons in the RTPC.\\

\begin{figure}[tb]
\centering
\includegraphics[scale=0.35]{fig/RTPC_2.png}
\caption[]{A schematic drawing of a $^{4}He$ track (in green) traversing the 
drift region, with the drift paths followed by the electrons (in black). } 
\label{fig:RTPC_signals}
\end{figure}

@@

The drift paths are the trajectories which an electron follows in the gas. The 
standard software to calculate drift paths is the MAGBOLTZ program 
~\cite{MAGBOLTZ}. For its calculations, MAGBOLTZ needs to know the detector's 
geometry, the exact composition of the gas mixture and of course the electric 
and the magnetic fields. We used such calculations as a first calibration, but 
as can be seen with the drift speed, conditions are far from stable in the 
chamber. Moreover, because we use of a thin foil as a cathode, the geometry 
knowledge is limited to a millimeter precision. These problems, already 
encountered for the BoNuS RTPC calibration (ref), have motivated the 
acquisition of specific calibration runs. These are taken with lower energy 
electron beam (1.20 and 1.27 GeV) to enhance the cross section of the elastic 
process ($e ^{4}He \rightarrow e ^{4}He$). In this process the knowledge of the 
electron kinematic gives us the helium nuclei kinematic and therefore allow us 
to calibrate our drift paths independently of our knowledge of the exact 
conditions in the chamber.

@@

\subsection{Noise Rejection}

@@

For the energy deposit, $\frac{dE}{dx}$ is calculated in this way:
\begin{equation}
 \left\langle \frac{dE}{dX} \right\rangle= \frac{\sum\limits_{i} \frac{ADC_{i}}{G_i}}{L}
\end{equation}
Where the sum runs over all the hits of the track, $G_{i}$ is the gain of 
the associated pad, and $L$ is the visible track length in the active drift 
volume.

>>>>

The first implementation of a radial TPC with JLab-CLAS spectrometer has been 
performed by the BoNuS experiment \cite{BONUS} in 2005. The success of the 
BoNuS-RTPC in detecting the slow protons motivated the development of this new 
RTPC. For the channels of interest in CLAS-EG6 experiment, the recoiled 
$^{4}$He nuclei have momentum per charge around 150 MeV/c. The detection of 
these low-energy nuclei was the primary motivation for designing this detector.

\section{CLAS-EG6 RTPC design} \label{sec_design}
The design of CLAS-EG6 RTPC has been chosen according to physics and 
experimental considerations. At 6 GeV incident electron beam energy, the recoil 
$^{4}$He nuclei, from the coherent DVCS channel, have an average momentum (per 
charge) around 125 MeV/c, while the "standard" CLAS detects charged particles 
with a threshold of 250 MeV/c. On the experimental site, the chosen design has 
to fit within the available space inside a 5 Tesla Solenoid magnet that 
surrounds the target \cite{Hyon-suk}. Figure \ref{fig:RTPC2} shows an 
experimental view of the RTPC before being inserted into the solenoid.

@@

   \item The first gas gap extends from 3 mm to 20 mm radial distances. It is 
      filled with $^{4}$He gas at 1~atm. During run, this region is swarmed by 
      M\o ller electrons induced by the beam, such that filling this region 
      with a light gas like $^{4}$He minimizes secondary interactions. This 
      region is surrounded by a 4 $\mu$m thick window made of aluminized Mylar 
      and connected to ground.                                                                
   \item The gap region extends between 20~mm and 30~mm and is filled with a 
      gas mixture of 80$\%$ Neon and 20$\%$ Dimethyl Ether (DME). This region 
      is surrounded by a 4~$\mu$m thick window made of aluminized Mylar, which 
      serves as the cathode.

@@

We can measure the drift speed using the tracks detected in the RTPC, in figure 
\ref{fig:RTPC_signals} we represent a typical $^{4}$He track (in green). After 
it causes ionization in the drift region, the released electrons (in black) 
drift to the detection plane under the effect of the electric field. The 
electrons released close to the cathode take the most time to reach the readout 
pads while the geometrical symmetry insure they always travel the same 
distance. So by identifying the maximum TDC measured, we can infer the drift 
speed of the electrons in the RTPC.\\

\begin{figure}[tb]
\centering
\includegraphics[scale=0.35]{fig/RTPC_2.png}
\caption[]{A schematic drawing of a $^{4}$He track (in green) traversing the 
drift region, with the drift paths followed by the electrons (in black). } 
\label{fig:RTPC_signals}
\end{figure}

@@

The drift paths are the trajectories which an electron follows in the gas. The 
standard software to calculate drift paths is the MAGBOLTZ program 
~\cite{MAGBOLTZ}. For its calculations, MAGBOLTZ needs to know the detector's 
geometry, the exact composition of the gas mixture and of course the electric 
and the magnetic fields. We used such calculations as a first calibration, but 
as can be seen with the drift speed, conditions are far from stable in the 
chamber. Moreover, because we use of a thin foil as a cathode, the geometry 
knowledge is limited to a millimeter precision. These problems, already 
encountered for the BoNuS RTPC calibration (ref), have motivated the 
acquisition of specific calibration runs. These are taken with lower energy 
electron beam (1.20 and 1.27 GeV) to enhance the cross section of the elastic 
process ($e^{4}$He$\rightarrow e^{4}$He). In this process the knowledge of the 
electron kinematic gives us the helium nuclei kinematic and therefore allow us 
to calibrate our drift paths independently of our knowledge of the exact 
conditions in the chamber.

@@

\subsection{Noise Rejection}
Two different characteristic noise signatures were identified and removed during track reconstruction.

The first was an oscillatory noise located early in the readout time window in many channels, shown in the top panel of Figure~\ref{fig:noise}.  The amplitude of the noise is not dissimilar to those of real tracks.  About N\% of the channels exhibit this noise signature.  Due to its unique time-energy correlation for a given channel, the noise could be removed on an event by event and channel by channel basis, without any loss of good signals and the result is illustrated in the bottom panel of Figure~\ref{fig:noise}.

@@

For energy deposition, the mean $\frac{dE}{dx}$ is calculated as
\begin{equation}
 \left\langle \frac{dE}{dX} \right\rangle= \frac{\sum\limits_{i} \frac{ADC_{i}}{G_i}}{L},
\end{equation}
where the sum runs over all the hits of the track, $G_{i}$ is the gain of 
the associated pad, and $L$ is the visible track length in the active drift 
volume.
